---
title: "interminer: synopsis"
author: "Nicolas Coutin"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo=FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
options(dplyr.print_min = 4L, dplyr.print_max = 4L)
library(interminer)
```

### Take interval regions and query sequence features overlapping with it:

```{r}
df <- im("flymine") %>% 
  im_regions("~/out.gff3", c("Exon","Intron"),"D. melanogaster") %>% 
  im_get_gff3()
```
1. `im()` specifies which intermine data warehouse to query against
2. `im_regions()` reads the gff3 file located at "~/out.gff3", formats the 
intervals for intermine queries. Also specify to look for ("Exon" and "Intron") 
overlapping`feature_types` within the `organism` "D. melanogaster".
3. `im_get_gff3()` sends the query request, collects the result and returns a 
data.frame object (as gff3).

```{r}
head(df)
```

Alternatively, write the results to a file:

```{r, eval= FALSE}
im("flymine") %>% 
  im_regions("~/out.gff3", c("Exon","Intron"),"D. melanogaster") %>% 
  im_get_gff3("introns-exons_overlapping_out.gff3")
```

`interminer` provides 4 results "getters":

- `im_get_gff3()` returns .gff3
- `im_get_fasta()` returns .fa
- `im_get_bed()` returns .bed
These 3 are limited to sequence feature types (i.e. the chosen query must return
sequence feature objects). All other queries use the more general:
- `im_get()`
